NumPy---Array Computation for Python

### 2020-01-10 body.tex
Minor changes
Add caption titles

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array-concepts}
  \caption{\fixme{PLACEHOLDER: This figure needs some text to describe
  it}
   }
  \label{fig:array-concepts}
\end{figure*}

@@

@@

@@

@@

%Suppose the matrix \code{A} is a 2-d array and the vector \code{x} is a 1-d array.  Then \code{A @ x} computes %the matrix-vector product $Ax$ and \code{x @ A} computes the vector-matrix product $x^\top A$.  This matrix %multiplication operation extends to higher-dimensions by treating the array as a stack of matrices.

%\begin{figure}
%  \centering
%  \includegraphics[width=\linewidth]{static/sketches/fancy-indexing}
%  \caption{\fixme{Indexing using arrays, or ``fancy indexing''.}
%   }
%  \label{fig:broadcasting}
%\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{static/sketches/reductions}
  \caption{\fixme{Reducing an array along one of several axes. Note:
  may want to fix to have right-hand axis system.}
   }
  \label{fig:reductions}
\end{figure}

@@

\fixme{Ralf will take a first pass on the section on 1/12.}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{static/sketches/duck-arrays}
  \caption{\fixme{Examples of so-called ``duck arrays'': arrays
  implemented by another library that behave like NumPy arrays, and
  support NumPy operations.  Through protocols, it is possible to have
  a call such as $\cos(\cdot)$ succeed on each of these.}}
  \label{fig:duck-arrays}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array-concepts}
  \caption{\textbf{Fundamental Array Concepts.}
    \textbf{a,} The NumPy array data structure ...
    \textbf{b,} Indexing ...
    \textbf{c,} Broadcasting ...
    \textbf{d,} Indexing with arrays ... combined with broadcasting ...
   }
  \label{fig:array-concepts}
\end{figure*}

@@

% shape > num. of axes and number of elements in each axis

@@

% on top of this structure we add a powerful, expressive syntax for indexing and element-wise
% calculations ....
% this high-level syntax allows us to be efficient (broadcasting) and implement in C for
% optimizing

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{static/sketches/reductions}
  \caption{\textbf{Reductions.} \fixme{Reducing an array along one of several axes. Note:
  may want to fix to have right-hand axis system.}
   }
  \label{fig:reductions}
\end{figure}

@@

% + interactivity
% users tend to "live in their data",
% interactivity and powerful, expressive syntax ... inspect, feel their way forward, experiment
% collect these into imperative or functional programs ....
% not that they never plan, often do ... but the ability to stopping "programming"
% and experiment is a key factor in why people use numpy ....

@@

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{static/sketches/duck-arrays}
  \caption{\textbf{Duck Arrays.} \fixme{Examples of so-called ``duck arrays'': arrays
  implemented by another library that behave like NumPy arrays, and
  support NumPy operations.  Through protocols, it is possible to have
  a call such as $\cos(\cdot)$ succeed on each of these.}}
  \label{fig:duck-arrays}
\end{figure*}
